\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{School of random department names} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge This is the title of the template report \\ \horrule{2pt} \\[0.5cm]

### 2018-06-06 Report/notes.tex
adding curves

>>>>

\subsection{more data}
\begin{figure}
	\centering
	\includegraphics[width=17cm]{picture/New_model/distance_versus_k.png}
	\caption{distance (infinite norm) between SSP of event model with 1E-10 epsilon termination and SSP of event model and PTH model using hybrid and explicit,$t=1$,median $\lambda$,$\epsilon=10^{-5}$}
	\label{fig:dist_versus_k}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=16cm]{picture/New_model/performance_versus_k.png}
	\caption{Computation time for different values of $k$. For about $k>200$, GSMP implementation starts outperforming all phase-typed computations, despite the GSMP implementation being relatively poorly optimized.}
	\label{fig:performance}
\end{figure}
